Evolution of precopulatory and postcopulatory inbreeding behaviour

### 2016-09-14 ms_pre_post.Rmd
Finish off draft of Discussion: Costs of polyandry and inbreeding avoidance

Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm as a consequence of sexual conflict [e.g., @Arnqvist2005a; @Parker2006]. <!--- Male harm --->

>>>>

Another type of cost relevant for polyandry and inbreeding strategy is risk of male harm caused by sexual conflict [e.g., @Arnqvist2005a; @Parker2006]. We assumed that males were passive in mating encounters with females, but inbreeding theory predicts that males should benefit from a higher tolerance of inbreeding than females, leading to sexual conflict over inbreeding [@Parker1979; @Parker2006; @Kokko2006; @Duthie2015a]. Females that express the choice to avoid inbreeding when mating might therefore pay a cost of harm caused by coercion expressed by related males. This cost might itself evolve over time as male harm coevolves with female resistance [@Ronn2007; @Perry2011; @Wang2015a], and costs might vary with interactions among male non-relatives and relatives because effects of kin selection are predicted to reduce harm caused by related male suitors [@Rankin2011a]. To predict evolution of polyandry and inbreeding strategy in populations characterised by active males and sexual conflict, consideration of male inbreeding strategy and coevolution between male harm and female resistance might therefore need to be considered explicitly.
